\cvsection{Extracurricular Activities}
\begin{cventries}
  \cventry
    {}
    {}
    {}
    {}
    {
      \begin{cvitems}           
        \item{\textbf{Internship in National Taiwan University Building \& Planning Foundation, Yilan, Jan 2016, Aug 2016 - Oct 2016} \\
         2016 Community Planning Onsite Tutor Plan, Yilan County Government.  }
        %%           
        \item{\textbf{Internship in Caixin Media, Beijing}\\
         Assistant Editor of Digital Media, focus on editing news and reports about Internet media like Digital Marketing or Social Media.%%
         }
         %%
        \item{\textbf{Leadership in Youth Communications Workshop, ChangChun}\\ %%
        - Responsible for the issues about cities renew in the Northeastern. \\%%
		- Part of work about reconstructing the library of LingXia Town Primary School after the flood in Baicheng, JiLin. %%
          }  
         %%                 
        \item{\textbf{Leadership in Cross-strait Workshop, Nanjing}\\
         Responsible for the issues about renew of Nanjing City.%%
         }
         %%
        \item{\textbf{Director of the Eastern, V-Teaching } \\ %%
        A NGO devoted to improving the rural education. \\ %%
        - Participant in the Co-Bridge project, aiming at providing public welfare platform for college students and NGO. \\ %%
        - Responsible for the college team propagation and TC Eastern affairs, brings cooperation with Foreign Language College of Jiangsu Univ, establish the innovation club. }
        %%                                              
        \item{\textbf{Volunteer of the First Female Sociologist Academic Forum, Nanjing}\\
         Responsible for the preparation for the forum and the study all the trip.}                                    
      \end{cvitems}
    }
        
\end{cventries}
