\cvsection{Research Experience}
\begin{cventries}
  \cventry   
    {Under the instruction of Prof. Shenglin Chang, Chairman of GIBP}
    {Regional Planning of PuJiang \& Pinling  }
    {PuJiang/ Pinling}
    {Jun. 2015- Jan. 2016}    
    {
      \begin{cvitems}
      	\item{
        - Take charge of Investigation of ChengJia Village with rich tea and Transformation of Tea House.  \\
        - Reform of Tea Ecological Factory in Pinling - Feitsui Reservoir Areas and Tea Areas.
        }
      \end{cvitems}
      }
      
  \cventry   
    {}
    {Culture Heritage Reservation of Train Fix Factory in Taipei.}
    {Taipei}
    {Mar. 2013 - June. 2015}    
    {
      \begin{cvitems}
        \item{ 
        To reserve and create the new life of the industry heritage, our team propose a plan including education, international communication, community development, jobs and activity platform after detailed fieldwork and survey.}
      \end{cvitems}
    }
    
    \cventry   
    {}
    {Reform of NTU-BP Building}
    {Taipei}
    {Sept. 2014 - Jan. 2015}    
    {
      \begin{cvitems}
        \item{
        To improve the inner space of the bldg, we make furniture by ourselves and hold activity to collect feedback from students.
        }
      \end{cvitems}
    }
    
    
    
    
        \cventry   
    {Under the instruction of Prof. Zhan HongYan, President at Institute of Urban Science, NJU}
    {Regional Planning of Jiangsu Mt.YouZi}
    {Nanjing}
    {May. 2013 - June. 2013}    
    {
      \begin{cvitems}
        \item{\textbf{}\\
         Take charge of six parts of the project including the planning of Fairy-tale town and Folk Customs Village.
        }
      \end{cvitems}
    }
    
    
    
   \cventry   
    {Under the instruction of Prof. Zhai XueWei, President at Institute of Social Psychology}
    {Director of University Undergraduates Innovative Training Program}
    {Nanjing}
    {May. 2012 - Apr. 2013}    
    {
      \begin{cvitems}
        \item{
        - Sponsored by National Undergraduate Innovation Program, Key Project of Nanjing University. \\%%
		- Investigate on the structure of power in economic behaviors included in network, system and culture. \\%%
		- Leader and chief participant, study on China New Town Development, the role of personal relationship in operation of economy, cluster analysis and factor analysis.
        }
      \end{cvitems}
    }
    
   \cventry   
    {Under the instruction of Prof. Peng , Ms Chen}
    {Director of Research on analysis and promotions of social workers’ current living and working conditions}
    {HouZaiMen Street,Nanjing}
    {Apr. 2011 - Dec. 2011}    
    {
      \begin{cvitems}
        \item{ 
		Leader and chief participant, study on community development grid system and job burnout.}
      \end{cvitems}
    }

\end{cventries}


